Software Clusterings with Vector Semantics and the Call Graph

### 2019-04-26 manuscript/manuscript.tex
Add LIMBO results

\begin{table*}
  \caption{Experimental Results for Linux 4.21 Codebase}
    \label{tab:evaluation}
    \begin{tabular}{lrrrrrr}
    \toprule
    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
    \midrule
    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2 & 33694\\
    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\

    LIMBO \cite{limbo} & 21 & & \\
    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\

    Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\paragraph{Experimental Setting} Our method was run on Linux 4.21,
consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
and Ward-Linkage \cite{ward} as well as ACDC and LIMBO ($B = 10, S = \infty$). The results are presented in Table \ref{tab:evaluation}. 
As ground truth we have used the first level directories as a target clustering and as input we have considered 
the modules of the one-top directories. 
For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
As a clustering distance metric we have used the MoJo metric, as proposed in reference \cite{mojo}. 
Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
multiple times and averaged the results.

>>>>

\begin{table*}
  \caption{Experimental Results for Linux 4.21 Codebase}
    \label{tab:evaluation}
    \begin{tabular}{lrrrrrr}
    \toprule
    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
    \midrule
    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725 & 1 & 2092 \\
    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412 & 19.0 & 1710 \\
    LIMBO \cite{limbo} & 21 & 50--1810 & 163 & 375 & 50  & 1482 \\

    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70 & 1138 \\

    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
    \midrule
    Ground Truth & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\paragraph{Experimental Setting} Our method was run on Linux 4.21,
consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
and Ward-Linkage \cite{ward} as well as ACDC and LIMBO with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
As ground truth we have used the first level directories as a target clustering and as input we have considered 
the modules of the one-top directories. 
For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
As a clustering distance metric we have used the MoJo metric, as proposed in reference \cite{mojo}. 
Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
multiple times and averaged the results.
